---
title: "Fantrax Report"
output:
  html_document:
    df_print: paged
---

```{r, echo = FALSE, message=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
library(tidyverse)
library(RColorBrewer)

setwd("C:/Users/Joe/Documents/R")
df_MD <- read.csv("Fantrax_Data.csv", header = TRUE)
FTeams_MD <- read.csv("Fantrax_Agg_Data.csv", header = TRUE)

```

### Stats going into gameweek `r max(df_MD$GP)` 
*All stats are for outfielders only, with more than 20 mins game time*

***
#### Most favourable matchups
*sum total difference between each players league team position and their opponents league team position*

```{r, echo = FALSE, fig.height = 6, fig.width = 10}

Colours <- brewer.pal(length(unique(FTeams_MD$Team)), "Paired")

ggplot(FTeams_MD, aes(x=reorder(Team, Total_PosDif, FUN=mean), Total_PosDif, fill=Team)) +
      geom_bar(stat="identity") + labs(x = "Teams", y = "Sum Table Difference") +
      geom_text(aes(label = round(Total_PosDif,2)), position=position_dodge(width=0.9), vjust=-0.25) + 
      scale_fill_manual(values = Colours)
```

***
#### Best squad (inc bench)
*Distribution of the FP.G of all 14 outfielders for each team. Ordered by mean.*

```{r, echo = FALSE, fig.height = 6, fig.width = 10}

temp <- subset(df_MD, Status!= "W (Fri)" & Status!= "W (Sat)" & Status!= "W (Sun)" & 
                        Status!= "W (Mon)" & Status!= "W (Tue)" & Status!= "W (Wed)" &
                        Status!= "W (Thu)" & Status!= "FA")

Colours <- brewer.pal(length(unique(FTeams_MD$Team)), "Paired")

p <- ggplot(temp, aes(x=reorder(Status, FP.G, FUN=mean), fill=Status,  y=FP.G))
p + geom_boxplot(coef = 5) + labs(x = "Teams", y = "FP.G") + 
      scale_fill_manual(values = Colours)

```

***
#### Best chance creators
*Key passes per 90 by Assists per 90*

```{r, echo = FALSE, fig.height = 6, fig.width = 10}

temp2 <- subset(df_MD, Status!= "W (Fri)" & Status!= "W (Sat)" & Status!= "W (Sun)" & 
                        Status!= "W (Mon)" & Status!= "W (Tue)" & Status!= "W (Wed)" &
                        Status!= "W (Thu)" & Status!= "FA")

Colours <- brewer.pal(length(unique(FTeams_MD$Team)), "Paired")

p <- ggplot(temp2, aes(A.90, KP.90, colour = Status)) +
        geom_point() + scale_fill_manual(values = Colours) +
        geom_text(
          aes(label = Player),
          check_overlap = T,
          adj = -0.1,
          vjust="inward"
        ) +
          coord_flip(clip = "off")

p + theme_classic()
```

#### Best goal scorers
*Shots on target per 90 by Goals per 90*

```{r, echo = FALSE, fig.height = 6, fig.width = 10}

temp3 <- subset(df_MD, Status!= "W (Fri)" & Status!= "W (Sat)" & Status!= "W (Sun)" & 
                        Status!= "W (Mon)" & Status!= "W (Tue)" & Status!= "W (Wed)" &
                        Status!= "W (Thu)" & Status!= "FA")

Colours <- brewer.pal(length(unique(FTeams_MD$Team)), "Paired")

p <- ggplot(temp3, aes(G.90, SOT.90, colour = Status)) +
        geom_point() + scale_fill_manual(values = Colours) +
        geom_text(
          aes(label = Player),
          check_overlap = T,
          adj = -0.1,
          vjust="inward"
        ) +
          coord_flip(clip = "off")

p + theme_classic()
```

***
#### Predicted scores (based on opposition league table position)
*Sum of the Top 10 players for each team where each players score is their FP/G adjusted depending on their opponents league table position*

```{r, echo = FALSE, fig.height = 6, fig.width = 10}

Colours <- brewer.pal(length(unique(FTeams_MD$Team)), "Paired")

ggplot(FTeams_MD, aes(x=reorder(Team, Top10_Total_PosAdjFP.G, FUN=mean), Top10_Total_PosAdjFP.G, fill=Team)) +
      geom_bar(stat="identity") + labs(x = "Teams", y = "Goal Difference Adjusted Prediction") +
      geom_text(aes(label = round(Top10_Total_PosAdjFP.G,2)), position=position_dodge(width=0.9), vjust=-0.25) +
      scale_fill_manual(values = Colours)
```
